%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{\en{Education}\fr{Formation}\sv{Utbildning}}

% English
\en{
	% PhD	
	\cventry{2013--Present}
	{PhD Program in Electrical Engineering}{KTH, Royal Institute of Technology}{Stockholm, Sweden}{}
	{Electric Power and Energy Systems}

	% Double Degree KTH	
	\cventry{2011--2013}
	{Master of Science in Electrical Engineering}{KTH, Royal Institute of Technology}{Stockholm, Sweden}{}
	{Double Degree program with a major in Electric Power and Energy Systems}
	
	% Supelec
	\cventry{2009--2013}
	{Diplôme d'Ingénieur in Electrical Engineering}{Supélec}{Gif-sur-Yvette, France}{}
	{One of France's prestigious Grandes Ecoles in its field of electrical and computer engineering.}
	
	% Clemenceau
	\cventry{2007--2009}
	{Classes Préparatoires (CPGE)}{Lycée Clemenceau}{Nantes, France}{}
	{MPSI, PSI: Equivalent to two years of higher education. Intensive preparation for the national entrance examinations for engineering schools}
	}

% Francais
\fr{
	% PhD	
	\cventry{2013--Présent}
	{Programme Doctoral en Génie Électrique}{KTH, Royal Institute of Technology}{Stockholm, Suède}{}
	{Spécialité stabilité et modélication de reseaux de transmission d'électricité}
	
	% Double Degree KTH	
	\cventry{2011--2013}
	{Double Diplôme en Génie Électrique}{KTH, Institut Royal de Technologie}{Stockholm, Suède}{}
	{Option Électrotechnique, axé sur les réseaux de transmission d'électricité.}
	
	% Supelec
	\cventry{2009--2013}
	{Diplôme D'ingénieur de l'\'Ecole d'\'Electricité}{Supélec}{Gif-sur-Yvette, France}{}
	{Première et deuxième années du cursus général. La spécialité a été effectuée à KTH.}
	
	% Clemenceau
	\cventry{2007--2009}
	{Classes Préparatoires}{Lycée Clemenceau}{Nantes, France}{}
	{MPSI, PSI}
	}

% Svenska
\sv{
	% PhD	
	\cventry{2013--Present}
	{Double Degree in Electrical Engineering}{KTH, Royal Institute of Technology}{Stockholm}{}
	{Electric Power Engineering}
	
	% Double Degree KTH	
	\cventry{2011--2013}
	{Double Dipl\^ome}{KTH, Institut Royal de Technologie}{Stockholm}{}
	{Option \'Electrotechnique, axé sur les réseaux de transmission d'électricité.}
	
	% Supelec
	\cventry{2009--2013}
	{Diplôme D'ingénieur de l'\'Ecole d'\'Electricité}{Supélec}{Gif-sur-Yvette, France}{}
	{Première et deuxième années. La fin du cursus a été effectuée à KTH.}
	
	% Clemenceau
	\cventry{2007--2009}
	{Classes Préparatoires}{Lycée Clemenceau}{Nantes, France}{}
	{MPSI, PSI}
	
	
	}