%----------------------------------------------------------------------------------------
%	o WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{   \en{Experience}
            \fr{Expérience}
         	}

\subsection{\en{Vocational}
            		\fr{}
            		}

\en{
    \cventry{Aug. 2018\\ Present}{Scientific Engineering Associate}{LBNL}{Berkeley, CA}{USA}{Participated in numerous research projects at Grid Integration Group of the Energy Storage \& Distributed Resources Division:
    \begin{itemize}
            \item Prepared Power Hardware-in-the-Loop experiments for several projects with PV inverters,
            \item Developed and implemented several software projects in Python.
    \end{itemize}}
    \cventry{Jan. 2018\\ May 2018}{Visiting Researcher, Affiliate}{LBNL}{Berkeley, CA}{USA}{Visit at the Grid Integration Group of the Energy Storage \& Distributed Resources Division as part of my PhD studies:
    \begin{itemize}
            \item Assisted the development of a \textsc{Modelica} model for time of use tarifs for PVs in California.
    \end{itemize}}
	\cventry{March 2013\\ June 2013}{Research Engineer}{KTH}{Stockholm}{Sweden}{Participated in the \textsc{iTesla} project with the developement of a \textsc{Modelica} power system component library and the development of a model calibration toolbox:
	\begin{itemize}
		\item Developed wind turbine models in \textsc{Modelica}.
	\end{itemize}}
}

\fr{}

\subsection{\en{Miscellaneous}
                    \fr{Autres}
                    }

\en{
	\cventry{July 2010}{Summer Intern}{OCP}{Nantes}{France}{}
	\cventry{2007--2010}{Front desk agent - Summer job}{Mutualit\'e Retraite}{Nantes}{France}{}
	\cventry{Nov. 2009}{Phone prospection}{Sup\'elec Foundation}{Gif-sur-Yvette}{France}{}
}

\fr{
    \cventry{Juil. 2010}{Stage Opérateur}{OCP}{Nantes}{France}{Gestion d'un retour de syrops pour enfants.\\}
    \cventry{2007--2010}{Front desk agent - Summer job}{Mutualit\'e Retraite}{Nantes, France}{}{Answering the phone and welcoming visitors in the facility.\\Worked in three different elder care facilities.}
    \cventry{Nov. 2009}{Phone prospection}{Sup\'elec Foundation}{Gif-sur-Yvette, France}{}{Gathering financial contribution from the Sup\'elec Alumni for the school's foundation.}
}


